---
title: "SimpLinR Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(SimpLin)
```

SimpLin is a package that can be used to do perform simple linear regression.

The function, `SimpLinR`, takes in two numeric vectors as argument. The first argument, `x`, is your data, and the second argument, `y`, is your response.

The function returns a list containing the following outputs:

 - Coefficient estimates $\hat \beta_0$ and $\hat \beta_1$.
 - Standard errors and confidence intervals associated with the estimates.
 - Predicted values $\hat y$.
 - The residuals $e$.
 
Let's create a dataset to show how it works.
 
```{r}
set.seed(100)
beta0 = 3
beta1 = 1.5
n = 100
x = rnorm(n, 0, 1)
e = rnorm(n, 0, 2)
y = beta0 + beta1 * x + e

model = SimpLinR(x, y)
```

We can access the estimated coefficients of the returned list, which we've called `model`, by calling `model$coefficients`. The first entry is the estimate of the intercept, and the second entry is the estimate of the slope.

```{r}
paste("The intercept estimate is", round(model$coefficients[1], 3))

paste("The slope estimate is", round(model$coefficients[2], 3))
```

We can access the predicted values by calling `model$predicted`. Here, we plot the fit alongside the raw data:
 
```{r}
plot(x, y)
lines(x, model$predicted, col  = "red")
legend("topleft", legend=c("Predicted Fit"),
       col=c("red"), lty = 1, cex=0.8)
```

We can also extract the residuals to assess the normality of the errors:

```{r}
plot(model$residuals, model$predicted)
```

Finally, we can check how confident we are in our estimates by calling `model$SE` and `model$CI` to get the standard errors and confidence intervals, respectively.

```{r}
model$SE
model$CI
```

In this case, both confidence intervals contain the true parameter values.
